---
title: "Activity: Street or Road?"
author: "Alvin Chen"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(tidyverse)
library(esquisse)

#load in the data here 
# we will only be using the "street-addresses.csv" file from the text
download.file(url="https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv", destfile = "street_adresses.csv")
Addresses <-
  read.csv("street_adresses.csv")

```

## Recreate Solved Example using `sample(50)`

```{r}
# get sample of 50 adresses
Sample <-
  Addresses %>%
  sample_n(size = 50)

# box is better pattern
pattern <- "BOX\\s+(\\d+)"

# cases that match PO Box
Matches <- 
  Sample %>%
  filter(grepl(pattern, address))

# cases that don't match
Dont <- 
  Sample %>%
  filter( !grepl(pattern, address))

# pull out pattern for box 
BoxNumbers <- 
  Sample %>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)

```

## Recreate Soved Example using the entire `Address` data set

```{r}
# identify pattern
pattern <- "BOX\\s+(\\d+)"

# find cases that are boxes 
Matches_all <- 
  Addresses %>%
  filter(grepl(pattern, address))

# find cases that arent
Dont_all <- 
  Addresses %>%
  filter( !grepl(pattern, address))

# pull out bix numbers for entire set
BoxNumbers_all <- 
  Addresses %>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
# identify pattern
pattern <- "BOX\\s+(\\d+)"

# find cases that are boxes 
Matches_all <- 
  Addresses %>%
  filter(grepl(pattern, address))
```

There are 11,100 cases that are PO boxes.

## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)" #set pattern to extract 
LeftOvers <-  #creates new Data Frame LeftOvers
  Addresses %>%  #utilizes Addresses data set to filter through
  filter( !grepl(pattern, address),  #checks if address doesn't contain pattern
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address), #checks if address doesn't end with space then APT or UNIT and numbers after.
          !grepl(" BOX ", address) #checks if address doesn't contain the string BOX
          )
```

Used comment Method to explain each line 

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}

pattern2 <- "(AVE|BLVD|LN)" #set pattern to extract 
leftovers2 <- #creates new Data Frame LeftOvers2
  Addresses %>% #utilizes Addresses data set to filter through
  filter(!grepl(pattern2, address), #checks if address doesn't contain pattern
    !grepl("\\sAPT|UNIT\\s[\\d]+$", address), #checks if address doesn't end with space then APT or UNIT and numbers after.
    !grepl(" BOX ", address) #checks if address doesn't contain the string BOX
  )

```

Used comment Method to explain each line 

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r} 

# get all adresses that meet pattern2
address_count <-
  Addresses[!Addresses$address %in% leftovers2$address, ]

# make match_address into dataframe
match_address <-
  data_frame(address_count)

# total the number of times each road word occurs 
road_num <- 
  table(str_extract(match_address$address_count, pattern2))

#create DF table with the number each road word occurs
pt2_result <-
  data.frame(road_end = names(road_num),
  Count = as.numeric(road_num),
  stringsAsFactors = FALSE)

# arrange in decending order 
pt2_sorted <-
  arrange(pt2_result, desc(Count))

# display
head(pt2_sorted)


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}
ggplot(pt2_sorted, aes(x = reorder(road_end, -Count), y = Count)) +
  geom_col(fill = "#112446") +
  theme_minimal() +
  xlab("Street Endings") +
  ylab("Count") +
  ggtitle("Street Ending Popularity in Decending Order")

```

#### Additional Question 3: Comment on any patterns you see

A pattern that I notice is that Ave is is the most commone out tof the three and BLVD is the least populular with signifigantly less usages.
